Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-13 Manuscript/proof_outline.tex
another small change

\todo[inline]{Rename the todo! And replace by the version about contents?}

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
  theorem countably_additive_of_todo
    (hC : SetRing C)
    (m : ∀ s : Set α, s ∈ C → ℝ≥0∞)
    (hm_ne_top : ∀ {s} (hs : s ∈ C), m s hs ≠ ∞)
    (hm_add : ∀ {s t : Set α} (hs : s ∈ C) (ht : t ∈ C),
      Disjoint s t →
      m (s ∪ t) (hC.union_mem hs ht) = m s hs + m t ht)
    (hm : ∀ ⦃s : ℕ → Set α⦄ (hs : ∀ n, s n ∈ C),
      Antitone s → (⋂ n, s n) = ∅ →
      Tendsto (fun n => m (s n) (hs n)) atTop (nhds 0))
      ⦃f : ℕ → Set α⦄ (h : ∀ i, f i ∈ C) (hUf : (⋃ i, f i) ∈ C)
      (h_disj : Pairwise (Disjoint on f)) :
    m (⋃ i, f i) hUf = ∑' i, m (f i) (h i)
\end{minted}

>>>>

\todo[inline]{Rename the todo! \xout{And replace by the version about contents?}}

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
  theorem countably_additive_addContent_of_todo
  (hC : SetRing C)
  (m : AddContent C)
  (hm_ne_top : ∀ {s} (_ : s ∈ C), m s ≠ ∞)
  (hm : ∀ ⦃s : ℕ → Set α⦄ (_ : ∀ n, s n ∈ C),
    Antitone s → (⋂ n, s n) = ∅ →
    Tendsto (fun n => m (s n)) atTop (nhds 0))
    ⦃f : ℕ → Set α⦄ (hf : ∀ i, f i ∈ C) (hUf : (⋃ i, f i) ∈ C)
    (h_disj : Pairwise (Disjoint on f)) :
  m (⋃ i, f i) = ∑' i, m (f i) 
\end{minted}
